Software Citation Principles

### 2016-03-21 sc-principles/software-citation-principles.tex
Software Sustainability Institute

Some of the most actionable work has come from the NSF Software Infrastructure for Sustained Innovation (SSI) program in the form of blog posts written by their community fellows:

>>>>

Some of the most actionable work has come from the Software Sustainability Institute (SSI) in the form of blog posts written by their community fellows:
